### 2014-02-24 paper/retrofit.tex
Get step back in.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

>>>>

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (t, ldots) @= CE[e] .-> iconf iS (sched step (t, ldots))
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}
